Multifidelity Approximate Bayesian Computation with Sequential Monte Carlo Parameter Sampling

### 2020-01-30 paper/article.tex
Fix arxiv refs and subject codes and figures
Refer to JUQ in abstract

\documentclass[review,demo]{siamonline190516}

@@

\include{shared}

@@

\begin{abstract}
Multifidelity approximate Bayesian computation (MF-ABC) is a likelihood-free technique for parameter inference that exploits model approximations to significantly increase the speed of ABC algorithms~(Prescott and Baker, 2020).
Previous work has considered MF-ABC only in the context of rejection sampling, which does not explore parameter space particularly efficiently.
In this work, we integrate the multifidelity approach with the ABC sequential Monte Carlo (ABC-SMC) algorithm into a new MF-ABC-SMC algorithm.
We show that the improvements generated by each of ABC-SMC and MF-ABC to the efficiency of generating Monte Carlo samples and estimates from the ABC posterior are amplified when the two techniques are used together.
\end{abstract}

\begin{keywords}
SIAM Journals, Documentation
\end{keywords}

\begin{AMS}
00A20
\end{AMS}

>>>>

\documentclass[review]{siamonline190516}

@@

\include{shared}
\allowdisplaybreaks

@@

\begin{abstract}
Multifidelity approximate Bayesian computation (MF-ABC) is a likelihood-free technique for parameter inference that exploits model approximations to significantly increase the speed of ABC algorithms~(Prescott and Baker, JUQ, 2020).
Previous work has considered MF-ABC only in the context of rejection sampling, which does not explore parameter space particularly efficiently.
In this work, we integrate the multifidelity approach with the ABC sequential Monte Carlo (ABC-SMC) algorithm into a new MF-ABC-SMC algorithm.
We show that the improvements generated by each of ABC-SMC and MF-ABC to the efficiency of generating Monte Carlo samples and estimates from the ABC posterior are amplified when the two techniques are used together.
\end{abstract}

\begin{keywords}
Bayesian inference, likelihood-free methods, stochastic simulation, multifidelity methods, sequential Monte Carlo
\end{keywords}

\begin{AMS}
62F15, 65C20, 65C60, 93B30
\end{AMS}
